{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-08 documents/background.tex
Restructuring, maybe?
words

@@

bona fide clinically useful effect

@@

%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
From a pessimistic energetic perspective,  !!! we know what the spring constant k should be !!!
. We can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass.
, where 0.1 angstrom is derived from the lipid MD simulation. [that's not right!]

@@

Unfortunately, the experimental results on M13 appear to have completely failed replication by Wigle \cite{No2011}, and those on lymphocytes do not agree with existing literature by two orders of magnitude \cite{Targeted2002}, observing that over 1 TW of incident power is required to reproduce the effects by .

1 TW / (100 ps / 0.3 ps) = 3 GW

@@

However, there equally appear to be no fundamental reasons why some small-molecule drug could not bind to the wrong receptor, why

@@

Notice that a non-zero resonant frequency
requires $\beta = b/(2m) \i-t \sqrt{2}$ \cite{Driven}

@@

\section{Matters to consider in the design of experiments and the evaluation of literature}

\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and debunking of non-classical damping hypotheses}

Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to produce a resonance-like peak.

Such an effect is so unexpected - Bigio et al describe it as “astonishing”. Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect. This result seems to have triggered a large amount of work to model this interaction, and various other interactions, in an attempt to explain the observed resonance.

At first blush, such an explanation does not seem unreasonable. In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).

Treating the interaction between the first few solvent layers surrounding some biological structure is indeed quite difficult; we encountered this in trying to setup MD This can be seen in [MD paper], so it is reasonable that continuum-like damping assumptions might break down.

In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges strikingly from the continuum hypothesis toward zero.

@@

In Bigio’s words “Extreme care”. Because it involves a differential measurement of two samples.

Hagmann and Gandhi \cite{Substitution1982}

@@

In the case of our crude, amateurish equipment, by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at almost any frequency we liked. We were able to produce many candidate peaks even in pure water.

@@

However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectroscopy if it is well conducted. The Sun group seem very competent experimenters, and the experiments are very well conducted; but history would seem to suggest that we take some degree of caution.

@@

We do not intend to denigrate the work or otherwise cast aspersions on the authors of the mentioned papers; their experiment extremely well-designed and performed.

However, since the result is unexpected, we would like to mention a few means by which the effect described could be achieved without strong non-thermal coupling.

@@

@@

@@

Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\

Other studies (Yang et al, Hung et al, Sun et al) then appear to demonstrate experimentally that - due to this effect and the favorable combination of envelope and genome net charge, envelope and capsid yield stress, mass distribution, and overall stiffness - certain viruses can  apparently be made to ring up, leading their envelope to shatter, when exposed to intense but ostensibly safe CW tones in the X-band - very much like a singer might shatter a wine glass.\\

Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature. For instance, the very paper (Edwards) which spurred development of the hydration-layer damping hypothesis used to explain these results, is has been quite\cite{Resonances1987} definitively\cite{Microwave1993a} shown to be an artifact, one which we unfortunately have not excluded in our study.\footnotemark \ In fact, even in light of the fine evidence that the other groups have collected, and the poor-quality data we have collected, we are still not entirely convinced that this effect exists - but perhaps this skepticism is unjustified.\\

\footnotetext{we should verify, based on simple solvated sphere damping, whether the damping is of the right order of magnitude}

We contribute almost nothing to the record (much of our discussion has already been covered by []), except by apparently replicating the effect in a T4 bacteriophage surrogate, using both microwave feedback and a luminometric beta-galactosidase infectivity assay. We appear to demonstrate that inactivation does not require 15 minutes, but is complete in less than 500 nanoseconds. This provides a headroom of some $10^6$ to all safety limits imposed by all known harm mechanisms, which can be traded for depth in tissue or distance in space. \\

@@

We briefly review the biological basis for the safety. There is solid in vitro and limited in vivo evidence of safety in this regime.

We briefly examine three applications. All depend significantly on what the microwave spectrum of SARS-NCoV-2 ends up being, which must be measured - or possibly reconstructed from existing whole-virion data or determined from coarse-grained MD simulation.

With refinements, our inexpensive pulsed microwave spectrometer can obtain the required absorption and threshold data with sufficiently concentrated specimens; but proper dielectric spectroscopy labs (or, in a pinch, swept-EPR/ESR equipment \st{when used improperly}) will provide a much more detailed spectrum. A slightly safer low-titer primary specimen may be usable to avoid BSL-3 requirements. \\

%
Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue. 
\\

[] notes that with a bit more effort, by harnessing the dispersive nature of tissue using modulated Brillouin precursors, it may be possible to remove the virus from the body altogether.\\

The mechanism also provides a few distinctive microwave signatures that may be useful for detection; it remains to be seen whether these can be discerned in practice.

The claims above are extraordinary. We do not provide the extraordinary quality of evidence required to support them. Consider: is it more likely that an undergraduate in his parent's basement, with no experience in biology or microwave design, has misinterpreted a blip from a cobbled-together machine, or that

expelling its viral contents into solution and

Not to be confused with pseudoscientific 'resonance therapies', nor reports of a connection with 5G communications.

This means that the technique is {\it selective}.

More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of. See below and supplemental.}

They demonstrate this with both a plaque and PCR assay, finding good agreement with the theoretical model.\footnote{As we will discuss, there are a few issues with the experimental technique.; sham, blinding, and dosimetry demanded by [Vjl.] are not mentioned.}

\paragraph{Ramifications}\

\begin{autem}

	{\it autem}\\
	The previous paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.

\end{autem}

>>>>

 (of course, it turns out )

There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.

However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018].

In addition, what data remains in this category is of varying quality.

As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfectly conducted to offer any meaningful results.

So, turning to, we find an entirely new set of problems. This effect is presumed to depend on mechanical forces of the entire virus. The large scales of physical virology all but prevent all-atom simulations that include the genome, but the genome is essential to the effectiveness of this technique. The same reasons currently rule out simulations including chemical reactions, important for lipid oxidation effects. Attempts at coarse-graining require careful tuning \footnote{or "parameterizing" in MD parlance}, where slight mis-steps in problem setup can lead to unphysical effects that completely alter the conclusion, particularly where solvent polarization. The kind which can only be obtained through extensive hard-wrought expertise (which the author does not possess) and careful verification,

Multiscale or hybrid techniques would seem to offer one route out of this pickle. Simulating a small patch of lipid in explicit solvent, with the pressure provided by

The stymied writer turns to writing inconclusive high-level summaries which lack sufficient detail to be of true use.

@@

We put some

More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.

The experiments are competently designed and many orthogonal measurements are made to confirm the effect.

There are a few minor issues with the experimental technique; sham, blinding, and dosimetry demanded by Vjl. are not mentioned.

\lettrine{U}nfortunately, we later realized that for both the absorption cross section and the requires the virus, a structure with not more than $6 \times 10^8$ atoms, to have an effective charge of $q=10^7$. It is very difficult to account for such a charge by any known mechanisms.

% 300 MDa of hydrogen has 3e8 H atoms
% ((100 nm)^3 * (1000 kg/m^3))/((18.15 g/mol) / avogadroConstant)
% 600 MDa

While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}. We have not investigated this in any depth.

In another attempt to explain non-thermally, it is possible that this result could be explained by lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes; but this would not necessarily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.

We are thoroughly mystified by the data presented. For the purposes of this paper, we accept a working hypothesis that this does not represent a clinically useful effect - especially as the exposures required are close to - or greatly exceed - the thermal limit for safety.

In any case, this is a very interesting result, and should be replicated with better controls. Gordon Reuben's team appear to be on the case, so we will not address this regime, 100 V/m, 15 minute, 8 GHz, any further.

We leave this section here because it will be useful to inform us in the next section.

Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue.

One might be tempted to cite long wavelength of microwaves as an advantage. A UV photon is approximately the same wavelength as the virus itself;  In the case of, the wavelength is >> diameter, d

Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature. For instance, the very paper (Edwards) which spurred development of the hydration-layer damping hypothesis used to explain these results, is has been quite\cite{Resonances1987} definitively\cite{Microwave1993a} shown to be an artifact, one which we unfortunately have not excluded in our study.\ In fact, even in light of the fine evidence that the other groups have collected, and the poor-quality data we have collected, we are still not entirely convinced that this effect exists - but perhaps this skepticism is unjustified.\\

@@

%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
From an energetics perspective, we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass. With relatively sane choices of screened charge and resonant frequency, the energy per monocycle at 5 MV/m varies from 0.01 to 20 times the thermal energy $k_b T$.

@@

Unfortunately, the experimental results on M13 appear to have completely failed replication by Wigle \cite{No2011}, and those on lymphocytes do not agree with existing literature by two orders of magnitude \cite{Targeted2002}, observing that over 1 T$\text{W/m}^2$ of incident power is required to reproduce the effects by .

$1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$

@@

It is common for. However, non-zero resonant frequency requires the ratio of the the loss in energy to the surroundings to the mass, to be greater than $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.

@@

Indeed, relatively trustworthy time-domain spectroscopy of proteins \cite{Microwave1994} has found that the relaxation time is proportional to the molecular weight of the structure (of which viruses are perhaps the ultimate example), and can be as slow as 100 MHz in some cases.

@@

\clearpage
\end{multicols}
\section{Commentary on the Sun group results; matters to consider in the design of experiments and the evaluation of literature}

When confronted by an extremely surprising and novel result, it seems useful to consider precisely where deficiencies may lie, so that our follow up work might address these concerns; to consider all the ways in which the ultimate conclusion could be falsified; in this case, by exploring what ways the observed facts could be explained without invoking non-thermal mechanisms, so that scope for such explanations may later be reduced.

\begin{toolchain}
We must now stress decisively that, as with all scientific critique, this commentary must not be construed as a reflection on the quality of the original study, and especially not towards its authors.\\

We are adamant that, in all cases cited, we believe their studies were well designed and conducted: the authors went to considerable and sufficient lengths to demonstrate its validity. 
\end{toolchain}

\begin{fquote}[Professor David Baltimore][\cite{Issues2008}]
	The scientific literature is a conversation among scientists; we describe to each other what we have done, and we implicitly ask our colleagues to try to build on our results, testing their value and their ability to support a growing edifice.

	In fact, a scientist's first response upon reading a new paper may be to see a new interpretation, to conceive a different experiment that could provide a wholly new thrust for the paper. This is a thought process that is encouraged in all young scientists, and it is one of the driving forces in science.
\end{fquote}

\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and invalidation of non-classical damping hypotheses}

Edwards et al in a series papers in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to produce a resonance-like peak in the absorption spectrum.

Such an effect is so unexpected - Bigio et al describe it as “astonishing”. \\

Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect.

This result seems to have triggered a large amount of work, both theoretical and experimental\cite{Structure1989}, in an attempt to model this interaction, and various other similar interactions, in an attempt to explain the observed resonance.

At first blush, such an explanation does not seem unreasonable. In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm). Indeed, it is now well-known that the layers formed by explicit solvents have significant effect on the conformations of proteins.

In the case of a uniform rotating sphere\cite{Molecular1963}, for instance, continuum Einsten-Stokes drag and discrete molecular drag diverge completely!

@@

The same issue, where a resonance is reported using microwave spectroscopy and subsequently irreplicable has occurred many times in the past - with Hagmann and Gandhi \cite{Substitution1982}.

In Bigio’s words “Extreme care”. Because it necessarily involves performing differential measurement of two samples, subtracting an enormous background from a minuscule sample.

Of course, such subtraction and de-embedding are very common techniques in the

In terms of volume, the

%((120 nm)^3 * 10^13) / 50 ml = 0.035%

Whereas a 50 microliter pipette will have a volume tolerance of 2\%!

Indeed, a sample of on a diean E5000 dielectric resonator

The difficulty is that the loss tangent of water varies fro about 0.3 at 6 GHz to 0.45 at 10 GHz \cite{Metamaterial2015}. A microstrip might optimistically have a loss of 0.315 dB/cm - perhaps 2.5 or to 5\% power loss.

$$f = \frac{233}{\sqrt{e_r}\cdot{V^{1/3}}}$$

%((1e7 * (electron charge) * 100 V/m)^2 / ((2*pi*(5 GHz))^2 * 50 MDa) * (10^13 / ml) * (50 microliter)) / (100 ps) = 1.56628917 watts

% 1 nanonewton * 1 nanometer  * 10^13

@@

In the case of our (admittedly crude, amateurish equipment), by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at almost any frequency we liked. We were able to produce a candidate resonance even in pure water.

@@

However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectroscopy if it is well conducted; but history would seem to suggest that we take some degree of caution with such results.

@@

@@

Glass and water are not infrared transmissible; only the surface temperature of the sample can be measured.

@@

Electrochemical the presence of various ions

$20 \text{W/m}^2 * 6 minutes to \text{J/m}^2 = 7200 \text{J/m}^2$

@@

 $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\

@@

### 2021-02-08 documents/comment.tex
Writing, re-organizing references
words

Indeed, I have no conclusion as to whether the effect seen exists. The effect ultimately requires a 
fully atomistic treatment, involving a very subtle re-arrangement of the lipid bilayer; ample 
mechanisms for such an effect exist to account for Sun et al's observations. For instance, see 
Liburdy's observations of liposome leakage due to oxygen.

@@

The temperature is measured via a conventional infrared thermometer to be below the lipid melting point, but is otherwise uncontrolled. Previous experiments have shown that such readings are not sufficient to isolate non-thermal effects.

Figure 6 is then difficult to explain. If the effect is thermal, why would the peak of the inactivation curve lie correspond perfectly to the one obtained by spectroscopy? The gain flatness of the antenna and amplifier may

@@

@@

As noted in the papers, unlike other biological systems it's plausible that the virion would have modes that are at least very close to being under-damped. Burkhartsmeyer offer reasonable evidence for this (although resonance-like artifacts are not unheard-of in Raman spectroscopy).

@@

This has some pretty awesome implications if it is correct, but whether the small amplitude 
amplification factor associated with this effect will be important is not known to me.

@@

There is data to support a little-known "prompt" electroporation effect of viruses at 
some $10^7 \text{V/m}$. Single pulses along these lines are not obviously damaging, per NATO 
Research Task Group 189. With some optimization, a keyhole between the electroporation threshold 
for may be found.

@@

However, a carefully shaped pulse that matches the Cole-Cole dispersion relation of tissue 
(apparently, a sawtooth) appears to side-step Beer's law decay and drives the oscillator some 300x 
more strongly.

>>>>

Indeed, I have no conclusion as to whether the effect seen exists. The effect ultimately requires a 
fully atomistic treatment, involving a very subtle re-arrangement of the lipid bilayer; ample 
mechanisms for such an effect exist to account for Sun et al's observations. For instance, see 
Liburdy's observations of liposome leakage due to oxidation.

@@

The temperature is measured via a conventional infrared thermograph to be below the lipid melting point, but is otherwise uncontrolled. Previous experiments have shown that such readings are not sufficient to isolate non-thermal effects with continuous wave exposures.

Figure 6 is then difficult to explain. If the effect is thermal, why would the peak of the inactivation curve lie correspond perfectly to the one obtained by spectroscopy? The gain flatness of the antenna and amplifier may be an explanation.

@@

The fundamental idea of inducing mechanical stresses with large electric fields is quite interesting.

these lines are not obviously damaging to tissue, even in-vivo, per NATO 
Research Task Group 189.

Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped protein encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness with 120 pulses, about 500 nanoseconds each, at 3 MV/m. Electron microscopy demonstrates that the mechanism is irreversible damage to the capsid or envelope respectively and subsequent release of the core, and is somewhat unlike thermal treatment.

\begin{autem}
	Extreme care must be taken in interpreting the results of any one study in isolation, especially in this field.

	Though the temperature was monitored, In this observation, the thermal artifact cannot necessarily be completely discounted. The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids \cite{Thermal1999} and 50 C for envelopes\cite{Stability1985}}. \\ The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses. 
\end{autem}

Madiyar \cite{Manipulation2013} observe rapid permeabilization (likely through the slow, conventional electroporation mechanism) at a field of poorly-defined intensity up to about 10 MV/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus). \cite{AC2017}. Interestingly, the same effect is not observed in T4 bacteriophage.

@@

As noted in the papers, unlike other biological systems it's plausible that the virion would have modes that are at least very close to being under-damped. Burkhartsmeyer and the Reuben team offer reasonable evidence for this (although resonance-like artifacts are not unheard-of in Raman spectroscopy).

Indeed, relatively trustworthy time-domain spectroscopy of proteins \cite{Microwave1994} has found that the relaxation time is proportional to the molecular weight of the structure (of which viruses are perhaps the ultimate example), and can be as slow as 100 MHz in some cases.

@@

This has some pretty awesome implications if it is correct, but whether the small amplitude 
amplification factor associated with this effect will be of any utility is not known to me.

@@

Less than 5 to 10 nanoseconds (where membrane breakdown, ion diffusion, and thermal effects start to become significant at these fields, and any previous absorbed power has been dispersed in the solvent) but greater than about 10 picoseconds (covered by existing laser research) and electric fields between 0.1 MV/m (for which biological effects at these timescales are only barely plausible) and 20 MV/m (the production of pulses which strain credulity).

There is data to support a little-known "prompt" electroporation effect of viruses at 
some $10^7 \text{V/m}$.

%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
From an energetics perspective, we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass. With relatively sane choices of screened charge and resonant frequency, the energy per monocycle at 5 MV/m varies from 0.01 to 20 times the thermal energy $k_b T$.

Compare to ~5 $\times k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

@@

However, a carefully shaped pulse that matches the Cole-Cole dispersion relation of tissue 
(apparently, a sawtooth) appears to side-step Beer's law decay, and is able to drive the oscillator of the virus many times more strongly than might be expected.

### 2021-02-08 documents/detection.tex
words

\begin{autem}
	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent here was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.
\end{autem}

@@

\includegraphics[width=\textwidth]{x_gal.jpg}

>>>>

\begin{autem}
	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent on this problem was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.\\

	None of the techniques that we mention are even remotely novel, and we present only the barest of experiences with each.
	Indeed, the fluorescence technique that were eventually decided on is common practice for lysis detection; our use is not novel in the slightest.
\end{autem}

@@

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=0.3\textwidth]{x_gal.jpg}
	\caption{The very pretty opalescent blue culture caused by E. coli B trying to metabolize lactose in an X-gal $\beta$-galactosidase enzyme indicator.}
\end{figure}

### 2021-02-08 documents/lessons_learned.tex
goddamnit, going down the same path again...
words

\paragraph{Lessons Learned} \

@@

When to publish

One the one hand, there're some pretty good reasons to want embargoes, like the Ingelfinger rules - no need to lather up a furor just for some idle musings, and publishing too early is a terrible idea. In retrospect, it was extremely good that I did not make a fuss about some extremely positive data; it turned out to be an embarrassing mistake in

@@

\paragraph{Hall of Hubris} \

Lest our hats stop fitting

@@

Like many microwave semiconductor HBT or pHEMT MMICs, the HMC996 amplifier requires.

@@

>>>>

\section{Lessons Learned} \

Rather than focus effort on making marginal improvements to avoid errors in a certain technique, it may be better to find an experimental technique that is totally immune to these problems. Obviously this isn't always possible or practical.

Like many microwave semiconductor HBT or pHEMT MMICs, the HMC996 amplifier requires careful biasing (discussed in section blah), or else it destroys itself.

@@

When to publish?

One the one hand, there're some pretty good reasons to want embargoes, like the Ingelfinger rules - no need to lather up a furor just for some idle musings, and publishing too early is a terrible idea. In retrospect, it was extremely good that I did not make a fuss about (or obtain funding for the original ) some extremely positive data; it turned out to be an embarrassing mistake in a data analysis script.

@@

\subsection{Hall of Hubris} \

Lest our hats stop fitting - a reminder that arrogance, fallacious beliefs, etc can creep in at any point

@@

@@

Photomultiplier

"Does anyone know of a circuit that can discriminate color PMT"?

only works if scintillator

### 2021-02-08 documents/molecular_dynamics.tex
words

@@

Rather than use standard eigenmode-style normal-mode methods (ProDy), Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a really fantastic program. Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations. The initial "spring Note the non-zero y-intercept.

>>>>

combine spherical geometry PB with small lipid section

@@

Rather than use standard algebraic normal-mode methods (ProDy), Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a really fantastic program. Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations. The initial "spring Note the non-zero y-intercept.

### 2021-02-08 documents/old_garbage_for_later.tex
words

\documentclass[fleqn,10pt]{article}

\include{preamble}

\begin{document}

\subfile{title}

\begin{table}[h!]
	\centering
	\begin{tabular}{ |c|c|c|c| } 
		\hline
		col1 & col2 & col3 \\
		\hline
		& cell2 & cell3 \\ 
		& cell5 & cell6 \\ 
		& Negative & 5 \\ 
		\hline
	\end{tabular}

	\caption{Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts. Not thoroughly characterized. Repeatability between test conditions   Background was no. 
	The flurometer printed a constant stream of the integration, all within the random error between capture windows $\sigma=0.5$ kcounts. }
\end{table}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{pulse_exposure_setup.JPG}
	\caption{\\ \textit{Chengxiang} pulse exposure jig. pulser seen off the left. Autosampler Pulse shaping plate not shown. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
\end{figure}

\subfile{background}

\begin{figure}[H]
	\makebox[\textwidth][c]{
		\includegraphics[width=\textwidth*2]{chunk_4_line_2_1.png}
	}%
	\caption{Chunk 4, it.is Founda}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{chunk_4}
	\caption{
		\light{
		\\
		We've got a thing\\
		that's called\\
		{\it Radar Love}\\}
		We've got a wave\\
		in the air}
\end{figure}

ICNIRP 2020, Table 3, Basic Restrictions

\clearpage
{\Large \it The contenders}\\

@@

\subfile{safety}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
{\Large Modes of application}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Sensing}

There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].

However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.

Havelka \cite{Highfrequency2011} discuss microtubules.

With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.

However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:

$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$

which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.

% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W

\end{multicols}

{\color{red} speculation \} }

\subfile{brillouin_pulse_math}

%\paragraph{}

%\subfile{acknowledgement}

\subfile{charge}

\subfile{viscosity}

\subfile{molecular_dynamics}

\section{Appendix on microwave design}

\subfile{supplemental}

\section{Appendix on microbiology}

\subfile{fluorescence}

\subfile{sic_susceptor}

\subfile{detection}

\subfile{lessons_learned}

\nocite{*}

%\printbibliography[]
%\printbibliography[title={All references}]

\end{document}

>>>>

@@

ICNIRP 2020, Table 3, Basic Restrictions
.

We briefly review the biological basis for the safety. There is solid in vitro and limited in vivo evidence of safety in this regime.

We briefly examine three applications. All depend significantly on what the microwave spectrum of SARS-NCoV-2 ends up being, which must be measured - or possibly reconstructed from existing whole-virion data or determined from coarse-grained MD simulation.

With refinements, our inexpensive pulsed microwave spectrometer can obtain the required absorption and threshold data with sufficiently concentrated specimens; but proper dielectric spectroscopy labs (or, in a pinch, swept-EPR/ESR equipment \st{when used improperly}) will provide a much more detailed spectrum.
